\documentclass[12pt,letterpaper]{article}

\def\myauthor{Vikram Dhillon}
\def\mytitle{vd-vita}
\def\myemail{dhillonv10@knights.ucf.edu}
\def\myweb{opsbug.com}
\def\myphone{407-683-3076}
\def\mykeywords{
  vikram dhillon, 
  resume, 
  curriculum, 
  vita, 
  curriculum vita, 
  cv, 
  vikram, 
  dhillon, 
  pdg
}

\setlength\parindent{0pt}

\newenvironment{itemize*}%
{\begin{itemize}%
  \setlength{\itemsep}{0pt}}%
{\end{itemize}}

\usepackage{url}
\usepackage{fancyhdr}
\usepackage{lastpage}
%\usepackage{ocgtools}
\usepackage{enumitem}
\setlist{nolistsep,leftmargin=0.15in}
\usepackage[log-declarations=false]{xparse}
\usepackage[adobe-garamond]{mathdesign}
\usepackage[no-math]{fontspec}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage[margin=1.125in,top=1.375in,right=1in,left=2in]{geometry}
\usepackage[strict]{changepage}
\pagestyle{fancy}

\usepackage[
  ocgcolorlinks,
  urlcolor={[rgb]{0,0,0.54}},
  unicode,
  plainpages=false,
  pdfpagelabels,
  pdftitle={\mytitle},
  pdfauthor={\myauthor},
  pdfkeywords={\mykeywords}
]{hyperref}

% fix ocgcolor link breaking; thanks due to Benjamin Lerner (http://goo.gl/VZKR7M)
\makeatletter
\AtBeginDocument{%
  \newlength{\temp@x}%
  \newlength{\temp@y}%
  \newlength{\temp@w}%
  \newlength{\temp@h}%
  \def\my@coords#1#2#3#4{%
    \setlength{\temp@x}{#1}%
    \setlength{\temp@y}{#2}%
    \setlength{\temp@w}{#3}%
    \setlength{\temp@h}{#4}%
    \adjustlengths{}%
    \my@pdfliteral{\strip@pt\temp@x\space\strip@pt\temp@y\space\strip@pt\temp@w\space\strip@pt\temp@h\space re}}%
  \ifpdf
    \typeout{In PDF mode}%
    \def\my@pdfliteral#1{\pdfliteral page{#1}}% I don't know why % this command...
    \def\adjustlengths{}%
  \fi
  \ifxetex
    \def\my@pdfliteral #1{\special{pdf: literal direct #1}}% isn't equivalent to this one
    \def\adjustlengths{\setlength{\temp@h}{-\temp@h}\addtolength{\temp@y}{1in}\addtolength{\temp@x}{-1in}}%
  \fi%
  \def\Hy@colorlink#1{%
    \begingroup
      \ifHy@ocgcolorlinks
        \def\Hy@ocgcolor{#1}%
        \my@pdfliteral{q}%
        \my@pdfliteral{7 Tr}% Set text mode to clipping-only
      \else
        \HyColor@UseColor#1%
      \fi
  }%
  \def\Hy@endcolorlink{%
    \ifHy@ocgcolorlinks%
      \my@pdfliteral{/OC/OCPrint BDC}%
      \my@coords{0pt}{0pt}{\pdfpagewidth}{\pdfpageheight}%
      \my@pdfliteral{F}% Fill clipping path (the url's text) with current color
      \my@pdfliteral{EMC/OC/OCView BDC}%
      \begingroup%
        \expandafter\HyColor@UseColor\Hy@ocgcolor%
        \my@coords{0pt}{0pt}{\pdfpagewidth}{\pdfpageheight}%
        \my@pdfliteral{F}% Fill clipping path (the url's text) with \Hy@ocgcolor
      \endgroup%
      \my@pdfliteral{EMC}%
      \my@pdfliteral{0 Tr}% Reset text to normal mode
      \my@pdfliteral{Q}%
    \fi
    \endgroup
  }%
}
\makeatother
% end fixes

\newcommand{\ML}{\textsc{Matlab}}
\newcommand{\Simu}{Simulink}
\newcommand{\MLS}{\ML{}/\Simu{}}
\newcommand{\apdl}{\textsc{APDL}}
\newcommand{\ansys}{\textsc{Ansys}}
\newcommand{\fluent}{\textsc{Fluent}}
\newcommand\CPP{C/C\ensuremath{+}\ensuremath{+}}
\newcommand{\Star}{\textsc{Star-CCM\ensuremath{+}}}

\newcommand{\mhead}[1]{\leavevmode\marginpar{\sffamily\footnotesize #1}}
\newcommand{\rdate}[1]{{\addfontfeature{Numbers=OldStyle} \hfill #1}}
\renewcommand{\date}[1]{{\addfontfeature{Numbers=OldStyle} #1}}
\renewcommand{\labelitemi}{-} 

\setmainfont[
  Ligatures={TeX,Common},
  BoldFont={AGaramondPro-Semibold.otf}, % file name from the uploaded fonts needed here
]{AGaramondPro-Regular.otf} %file name from the fonts needed again

\setsansfont[
  Ligatures={TeX,Common},
  Letters=SmallCaps,
  Color=660000,
]{AGaramondPro-Regular.otf}

\makeatletter % fix for \hrulefill w/ mathdesign package
\def\hrulefill{\leavevmode\leaders \hrule height \rulethickness \hfill\kern\z@}
\makeatletter

\begin{document}\flushbottom

\pagestyle{fancy} \setlength\headwidth{6.5in}
\rhead{\textsc{vikram ~dhillon—cirriculum ~vitae—\thepage{} of \pageref*{LastPage}}} \cfoot{}
\thispagestyle{empty}
\begin{adjustwidth}{-1in}{}
{\Huge
  {\textsc{%
    {\addfontfeature{Style=TitlingCaps}V}\kern-1.5ptikram 
    {\addfontfeature{Style=TitlingCaps}D}hillon}
  }
}
\hfill\hfill\hfill
{
    \begin{minipage}[b]{2in}
    \flushleft \footnotesize 
    11315 Rouse Run Circle \\ 
    Orlando, FL~~32817
  \end{minipage}
  \hfill
  \begin{minipage}[b]{1.2in}
    \flushright \footnotesize 
    \href{}{Phone: \myphone} \\ %\texttt{}~
    \href{mailto: \myemail}{\myemail} \\
    \href{Blog: opsbug.com}{Blog: \myweb}
  \end{minipage}
}\par
\hrulefill
\end{adjustwidth}  
\reversemarginpar 
\setlength\marginparwidth{0.85in}
\smallskip


\mhead{Education}%
\textbf{University of Central Florida,} Orlando, Florida \newline
\emph{Bachlor of Science: \href{http://med.ucf.edu/biomed/academics/undergraduate-programs/bs-biomedical-sciences/}{Molecular Biology}} \rdate{\textcolor{magenta}{\textsc{2011}–\textsc{2015}}}

\begin{itemize*}
  \item {\href{http://www.cs.ucf.edu/research/bsb.php}{Bioinformatics Specialization}}
  \item Relavent Minors: \href{http://catalog.ucf.edu/content/documents/programs/Bioengineering_Minor.pdf}{Bioengineering}, \href{http://catalog.ucf.edu/content/documents/programs/Philosophy_Minor.pdf}{Philosophy }
  \item Advisor: \href{http://www.cs.ucf.edu/~xiaoman/}{Dr.~Xiaoman Shawn ~Li}
  \item Thesis: Introduction to Metabolic Disorders
  \item Relevant Coursework:\newline
    \begin{tabular}{ll}
      Biochemical Methods, & Quantitative Biological Methods \\
      Structural Analysis, & Sequence Analysis \\
      Advanced Physiology, & Virtual PhysioEx \\
      Clinical Neuroscience, & Clinical Endocrinology \\
      Immunobiology, & Microbial Metabolism \\
    \end{tabular}
   \item \textbf{Any relevant student records can be made available upon request}

\end{itemize*}

\bigskip

\mhead{Research \newline Experience}%

\textbf{Nanoparticle flow simulation,} University of Central Florida \newline
\emph{Under Robert Van Gorder.} \rdate{\textcolor{magenta}{\textsc{Sep.}~2011–\textsc{Feb. 2012}}}

\begin{itemize*} 
  \item Created a computational simulation of nanoparticle transport in a blood vessel under the influence of a magnetic field in COMSOL
  \item Learned about nanoparticles as drug-delivery systems and the therapeutic uses of targeted drug delivery
  \item Learned about numerical modelling of nanoparticles and algorithms for design of nanoparticle coagulation
\end{itemize*}

\smallskip
\smallskip

\textbf{Calcium-based repriming of Imatinib,} University of Central Florida \newline
\emph{Under Dr. Mohtashem Samsam.} \rdate{\textcolor{magenta}{\textsc{Summer 2012}}}

\begin{itemize*} 
  \item Wrote a short review on the pharmacological properties and function of Imatinib in the treatment of CML
  \item Learned about drug repriming as a tool to combat drug resistance in second or third generation resistant cell lines
  \item Learned about the two-hit hypothesis in cancer treatment and the crucial role of intracellular calcium in overcoming drug resistance
\end{itemize*}

\smallskip
\smallskip

\textbf{Functional Conservation of Enhancer Regions,} University of Central Florida and Sanford-Burnham Medical Research Institute \newline
\emph{Under Dr. Xiaoman Li.} \rdate{\textcolor{magenta}{\textsc{Fall}~2011–\textsc{2014}}}

\begin{itemize*} 
  \item Wrote algorithms to detect regions of genomic similarity (called motifs) across human and mice genome
  \item Combined statistically significant motifs together into motif-modules. Motif-modules turn out to be better predictors of cross-genomic conservation
  \item Transitioned to application of statistical significance to biological relevance of motifs - Determining conserved regions across human genome present in mice
  \item High conservation correlated with functional preservation in the genomes
\end{itemize*}

\smallskip
\smallskip

\textbf{Neoplastic Metastasis via Differential Splicing,} University of Central Florida \newline
\emph{Under Dr. Xiaoman Li.} \rdate{\textcolor{magenta}{\textsc{2014}–\textsc{present}}}

\begin{itemize*} 
  \item Generalized the statistical determination of functional conservation to a scoring mechanism
  \item Applied the scoring mechanism to scoring mutations
  \item Learned about exome-sequencing for cancer-datasets
  \item Applied scoring scheme to the exome-sequencing data to determine which mutations are statistically significant
  \item Linked the source of the significant mutations to alternative splicing
  \item Determined the link between the alternative splicing causing selective mutations in tumor micro-environment 
  \item Before the research could be published, another independent group published all the conclusions we had \href{http://www.ncbi.nlm.nih.gov/pubmed/25274489}{reached}
\end{itemize*}

\bigskip
\mhead{Research \newline Funding}%

\textbf{Research and Mentoring Program (RAMP),} University of Central Florida \newline
\emph{Type: Fellowship} \newline
\emph{Faculty Mentor: Dr. Xiaoman Li.} \rdate{\textcolor{magenta}{\textsc{2013}–\textsc{2015}}}

\begin{itemize*} 
  \item Research program at UCF supporting students for two years to start their research
  \item Supported my research under Dr. Li working on sequence conservation and motif modules
  \item Mentoring opportunities along with the research to guide young researchers on how to get started
\end{itemize*}

\smallskip
\smallskip

\textbf{Computational Inference of Microbial Community Structures from Environmental Shotgun Reads} \newline
\emph{Type: National Science Foundation Award [\href{http://www.nsf.gov/awardsearch/showAward?AWD_ID=1218275
}{No. 1218275}]} \newline
\emph{PI: Dr. Xiaoman Li.} \rdate{\textcolor{magenta}{\textsc{Summer 2014}}}

\begin{itemize*} 
  \item NSF Grant obtained by my PI 
  \item Supported my summer semester for a project on protein docking and modelling
  \item Editing and proofreading of the grant proposal was done by me
  \item First time for me being an active participant going through the entire life-cycle of applying for a grant and then receiving it
\end{itemize*}

\smallskip
\smallskip

\textbf{Young Entrepreneur and Scholar (YES) Scholarship Program,} University of Central Florida \newline
\emph{Type: National Science Foundation Award [\href{http://www.nsf.gov/awardsearch/showAward?AWD_ID=0806931}{No. 0806931}]} \newline
\emph{Faculty Mentor: Dr. Xiaoman Li.} \rdate{\textcolor{magenta}{\textsc{2015}–\textsc{present}}}

\begin{itemize*} 
  \item Supported my research under Dr. Li on alternative splicing mutations and the scoring mechanisms.  
  \item Also worked on a project in metagenomics using single-cell genomics
  \item The YES Program had three tracks: Research, Entrepreneurship or Industry Mentoring. For me, the best path was a combination of research and entrepreneurship which translated to me applying for the NSF I-Corps grant.
\end{itemize*}

\smallskip
\smallskip

\textbf{National Science Foundation Innovation-Corps Award} \newline
\emph{Type: National Science Foundation Award [\href{http://www.nsf.gov/awardsearch/showAward?AWD_ID=1347356}{No. 1347356}]} \newline
\emph{Faculty Mentor: Dr. David Metcalf.} \rdate{\textcolor{magenta}{\textsc{2015}–\textsc{present}}}

\begin{itemize*} 
  \item Part of the inaugural class of the NSF I-Corps program at UCF as the university became an I-Corps site
  \item Received funding from the NSF I-Corps program to learn how to commercialize research 
  \item Took a course on the Lean Launchpad methodologies for research commercialization
  \item Learned the foundations of evidence based entrepreneurship and the core of creating an innovative venture based around just an idea
\end{itemize*}

\bigskip

\mhead{Honors \& \newline Awards}%

\textbf{Invited reviewer to Apress}
\rdate{\textcolor{magenta}{\textsc{2015}}} 

\begin{itemize*} 
  \item Reviewer for advanced machine learning through R (statistical programming package)
  \item Currently an Editor for the topic of advanced machine learning
\end{itemize*}

\smallskip

\textbf{Showcase of Undergraduate Excellence}
\rdate{\textcolor{magenta}{\textsc{2015}}} 

\begin{itemize*} 
  \item First place in life sciences division
  \item Presented my research under Dr. Li on neoplastic progression due to alternative splicing mutations
\end{itemize*}

\smallskip

\textbf{SourceCode B46 Capstone Event Judge}
\rdate{\textcolor{magenta}{\textsc{2015}}} 

\begin{itemize*} 
  \item Invited judge for the K-5 student presentations
\end{itemize*}

\textbf{Semi finalist Business Model Competition}
\rdate{\textcolor{magenta}{\textsc{2015}}} 

\smallskip

\textbf{Florida Undergraduate Research Conference}
\rdate{\textcolor{magenta}{\textsc{2015}}} 

\begin{itemize*} 
  \item State-wide undergraduate conference: Poster presentation
  \item Presented my research on alternative splicing and the scoring mechanism
\end{itemize*}

\smallskip

\textbf{Sanford-Burnham Medical Research Institute Fellow}
\rdate{\textcolor{magenta}{\textsc{Summer 2014}}} 

\begin{itemize*} 
  \item Studied Protiomics in the Biomarker Discovery Lab under Dr. Shi-Jian Ding
  \item Designed algorithms for protein peak detection from mass-spectrometry data
\end{itemize*}

\smallskip

\textbf{Reactome Project Fellow}
\rdate{\textcolor{magenta}{\textsc{2014}}} 

\begin{itemize*} 
  \item National Recognition: Only undergraduate to be mentored by the Reactome team
  \item Worked under Dr. Lisa Matthews to learn how Reactome annotates and reviews the biological pathways
\end{itemize*}

\smallskip

\textbf{Pitch your idea: UCF Blackstone Launchpad}
\rdate{\textcolor{magenta}{\textsc{2014}}} 

\begin{itemize*} 
  \item Second place in the contest
  \item First cryptocurrency startup to come out of Blackstone Launchpad
\end{itemize*}

\smallskip

\textbf{Showcase of Undergraduate Excellence}
\rdate{\textcolor{magenta}{\textsc{2014}}} 

\begin{itemize*} 
  \item Second place in life sciences division
  \item Presented my research under Dr. Li on functional conservation of regulatory elements 
\end{itemize*}

\smallskip

\textbf{TEDxUCF Semi Finalist Presenter} \rdate{\textcolor{magenta}{\textsc{2013}}} 

\smallskip

\textbf{Share\LaTeX Advisory Program} \rdate{\textcolor{magenta}{\textsc{2013}}} 

\begin{itemize*} 
  \item National Recognition
  \item 1 of 8 selected from the US
\end{itemize*}

\smallskip

\textbf{ACS Florida Logo Contest Winner} \rdate{\textcolor{magenta}{\textsc{2013}}}

\begin{itemize*} 
  \item The American Chemistry Society (ACS) Florida Chapter did not have a proper logo so they organized a contest to obtain one
  \item Won the contest and gave ACS Florida their new logo!
\end{itemize*}

\smallskip

\textbf{Youngest student to take graduate class in Immunobiology at University of Central Florida} \rdate{\textcolor{magenta}{\textsc{2013}}} 

\textbf{Invited synbio4All Developer and Designer} \rdate{\textcolor{magenta}{\textsc{2012}}}

\begin{itemize*} 
  \item Part of trans-Atlantic collaboration with Paris-Descartes University 
  \item Teaching citizen scientists about synthetic biology
\end{itemize*}

\smallskip

\textbf{Dean's List: For a few semesters through my undergraduate career}
\rdate{\textcolor{magenta}{\textsc{2011}–\textsc{2015}}}

\bigskip

\mhead{Conferences}

\textbf{TED Talk: TEDxUCF}
\rdate{\textcolor{magenta}{\textsc{2015}}}

\begin{itemize*} 
  \item Presentation: Engineering human life
\end{itemize*}

\smallskip

\textbf{BSides Orlando}
\rdate{\textcolor{magenta}{\textsc{2015}}}

\begin{itemize*} 
  \item Presentation: Decentralized Resource Management
\end{itemize*}

\smallskip

\textbf{Florida Undergraduate Research Conference}
\rdate{\textcolor{magenta}{\textsc{2015}}}

\begin{itemize*} 
  \item Poster: Neoplastic Metastasis via Differential Splicing
\end{itemize*}

\smallskip

\textbf{Showcase of Undergraduate Excellence}
\rdate{\textcolor{magenta}{\textsc{2015}}}

\begin{itemize*} 
  \item Poster: Neoplastic Metastasis via Differential Splicing
\end{itemize*}

\smallskip

\textbf{CloudSpace Android Meetup}
\rdate{\textcolor{magenta}{\textsc{2015}}}

\begin{itemize*} 
  \item Presentation: Design and application of enterprise apps
\end{itemize*}

\smallskip

\textbf{CloudSpace Ruby Meetup}
\rdate{\textcolor{magenta}{\textsc{2014}}}

\begin{itemize*} 
  \item Presentation: Blogging engine using Jekyll
\end{itemize*}

\smallskip


\textbf{CloudSpace JavaScript Meetup}
\rdate{\textcolor{magenta}{\textsc{2014}}}

\begin{itemize*} 
  \item Presentation: MEAN stack
\end{itemize*}

\smallskip

\textbf{Open Web Application Security Project (OWASP)}
\rdate{\textcolor{magenta}{\textsc{2014}}}

\begin{itemize*} 
  \item Presentation: Blog like a hacker
\end{itemize*}

\smallskip

\textbf{International Conference on Quantitative Finance}
\rdate{\textcolor{magenta}{\textsc{2014}}}

\begin{itemize*} 
  \item Poster: Healthcoin Data Decentralization
\end{itemize*}

\smallskip

\textbf{BSides Orlando}
\rdate{\textcolor{magenta}{\textsc{2014}}}

\begin{itemize*} 
  \item Presentation:  Wrecking the ultimate defense: Human Body
\end{itemize*}

\smallskip

\textbf{Showcase of Undergraduate Excellence}
\rdate{\textcolor{magenta}{\textsc{2014}}}

\begin{itemize*} 
  \item Poster: Functional Conservation of Enhancer Regions
\end{itemize*}

\smallskip

\textbf{American Chemistry Society: National Conference}
\rdate{\textcolor{magenta}{\textsc{2014}}}

\begin{itemize*} 
  \item Poster: Synthesis and Preparation of PNIPAAm
\end{itemize*}

\smallskip

\textbf{AGILE: Orlando}
\rdate{\textcolor{magenta}{\textsc{2012}}}

\begin{itemize*} 
  \item Presentation: AGILE Software Design Principals
\end{itemize*}

\bigskip

\mhead{Publications}%

\textbf{Dhillon V.} Ethics of engaging in low-impact research. \textit{In preparation}. Undergraduate Research Journal, University of Central Florida.

\smallskip

\textbf{Dhillon V}, Li X (2015). Single-Cell Genome Sequencing for Viral-Host Interactions. J Comput Sci Syst Biol 8: 160-165. doi:10.4172/jcsb.1000183

\smallskip

Ding J, \textbf{Dhillon V}, Li X, Hu H (2014). Systematic discovery of cofactor motifs from ChIP-seq data by SIOMICS. doi:10.1016/j.ymeth.2014.08.006

\smallskip

\textbf{Dhillon V.} Role of Neutrophil Extracellular Traps (NETs) in Innate Immunity. \textit{Accepted}. Undergraduate Research Journal, University of Central Florida.

\smallskip

\textbf{Dhillon V.} Professional blogging and development with Jekyll. \textit{In press}.\textbf{Apress}. 

\bigskip

\mhead{Leadership \newline Experience}%

\textbf{Entrepreneurial Lead: HealthShares} 
\rdate{\textcolor{magenta}{\textsc{2015-Present}}}

\begin{itemize*} 
  \item Founder of HealthShares startup through NSF I-Corps program
  \item Currently the tech. lead, my position is in part responsible to the NSF-grant
\end{itemize*}

\smallskip

\textbf{Tech Inoculator: \href{http://increasingprobability.com/}{Increasing Probability} } 
\rdate{\textcolor{magenta}{\textsc{2015-Present}}}

\begin{itemize*} 
  \item Pioneered the idea of a \textit{technology inoculator} for the startup world
  \item In microbiology labs, before a culture is set for incubation, it is inoculated so that the bacteria can slowly adapt to the environment. 
  \item A tech inoculator is based on the same principle, before entering a tech incubator, the entrepreneurs may benefit greatly from a tech inoculator
  \item Main purpose of an inoculator is to give overview of the field, the latest technologies and their impact.
  \item Allows the entrepreneur to expand their mind and look at the problems they face daily from different angles.
  \item An accelerator provides immense growth opportunities for a startup but to get there, the entrepreneurs need to be inoculated into the culture, environment and available resources
\end{itemize*}

\smallskip

\textbf{iGEM@UCF: Officer} 
\rdate{\textcolor{magenta}{\textsc{2014}}}

\begin{itemize*} 
  \item Student Organization: Working on biotechnology challenges for iGEM competition
\end{itemize*}

\smallskip

\textbf{Mendeley User Groups} 
\rdate{\textcolor{magenta}{\textsc{2013}}}

\begin{itemize*} 
  \item Created two user groups containing the latest papers in the area:
  \item Nano-Oncology and Neuro Hardware
\end{itemize*}

\smallskip

\textbf{Florida Hospital Volunteer - Summer volunteering} 
\rdate{\textcolor{magenta}{\textsc{2012}–\textsc{2013}}}

\begin{itemize*} 
  \item First position in ER and OR shadowing
  \item Second position in Patient Admissions and data entry
\end{itemize*}

\bigskip

\mhead{Mentoring}%

Teaching Assistant: \textbf{Clinical Neuroscience} (Dr. Samsam)
\rdate{\textcolor{magenta}{\textsc{Spring 2015}}}

\smallskip

Teaching Assistant: \textbf{Chemistry I} (Dr. Heider)
\rdate{\textcolor{magenta}{\textsc{Fall 2014}}}

\smallskip

Mentor for \textbf{Society for Science: Science and Engineering Fair}
\rdate{\textcolor{magenta}{\textsc{Fall 2013}}}

\begin{itemize*} 
  \item Under Dr. Li to a high school student: Sonia Quadar
\end{itemize*}

\smallskip

Teaching Assistant: \textbf{Structural Analysis - Bioinformatics} (Dr. Li)
\rdate{\textcolor{magenta}{\textsc{Spring 2013}}}

\smallskip

Teaching Assistant: \textbf{Organic Chem 1} (Dr. Miles)
\rdate{\textcolor{magenta}{\textsc{Fall 2013}}}

\smallskip

Teaching Assistant: \textbf{Human Anatomy} (Dr. Samsam)
\rdate{\textcolor{magenta}{\textsc{Fall 2012}}}

\smallskip

Teaching Assistant: \textbf{Open Source Technologies} (Dr. Becka Morgan)
\rdate{\textcolor{magenta}{\textsc{Fall 2012}}}

\begin{itemize*} 
  \item Online course taught at Western Oregon University
  \item TAs placed through Ubuntu Developer's program
\end{itemize*}

\bigskip


\mhead{Software \newline Development}%

\textbf{Network Security Analyst.} HostDime
\rdate{\textcolor{magenta}{\textsc{Oct 2012}–\textsc{Mar 2013}}}

\begin{itemize*} 
  \item Big Data security and neural-net implementations
\end{itemize*}

\smallskip

\textbf{Server Analyst I.} HostDime
\rdate{\textcolor{magenta}{\textsc{Mar 2013}–\textsc{Aug 2013}}}

\begin{itemize*} 
  \item Load-analysis for servers and server management
\end{itemize*}

\smallskip

\textbf{Grsec Kernel Maintainer} On Sourceforge
\rdate{\textcolor{magenta}{\textsc{Spring 2013}}}

\begin{itemize*} 
  \item Custom bioinformatics kernel with multi-threading and additional security patches
\end{itemize*}

\smallskip

\textbf{Xenomai Kernel Maintainer} On Sourceforge
\rdate{\textcolor{magenta}{\textsc{Fall 2012}}}

\begin{itemize*} 
  \item Custom realtime kernel optimized for mass-spec proteiomics data analysis
\end{itemize*}

\smallskip

\textbf{Repo Admin: System Administrator} 
\rdate{\textcolor{magenta}{\textsc{Fall 2012}}}

\begin{itemize*} 
  \item Hosting and management of data-processing Perl scripts
  \item Management of over 1000 user-created repositories
\end{itemize*}

\smallskip

\textbf{Ubuntu Core developer} 
\rdate{\textcolor{magenta}{\textsc{2010}–\textsc{2011}}}

\begin{itemize*} 
  \item Volunteer effort
  \item Documenting the entire software release
\end{itemize*}

\smallskip

\textbf{eprentise Summer internship} 
\rdate{\textcolor{magenta}{\textsc{Fall 2010}}}

\begin{itemize*} 
  \item Data migration analyst
\end{itemize*}

\medskip

\emph{Working knowledge:}\newline%—comfortable using in a professional setting
\MLS{}, 
COMSOL Multiphysics,
Galaxy,
BLAST,
\CPP{}, 
Visual Studio, 
Microsoft Office Suite, 
Adobe Creative Suite, 
HTML/CSS, 
jQuery,
\LaTeX{},
Vim, 
Git,
SVN,
Arch Linux, 
Mac OS X, 
Windows 7/8

\medskip
\emph{Basic knowledge:}\newline%—would require some training/use to refresh my memory
Autodesk Products Suite, 
LabVIEW,
Modelica/Dymola

\rfoot{Updated: May 2015}

\end{document}
